Extrinsic Type Inference (DRAFT 2025-06-08)

### 2025-07-09 extrinsic_type_inference_paper/paper.tex
add comment on tree grammars and recursive types

To allow arbitrary mixing of constructions in pattern matching, the extrinsic type of constructions
must be abolished so that there is no intrinsic weakest type other than a top type.

In MLSub and algebraic subtyping \cite{}, forgoes the datatype mechanism.
Instead, it uses type inference to generates subtyping constraints and solve them, akin to unification in HM.

>>>>

To allow arbitrary mixing of constructions in pattern matching, the extrinsic type of constructions
must be abolished so that there is no intrinsic weakest type other than a top type. 
In MLSub and algebraic subtyping \cite{}, forgoes the datatype mechanism.
Instead, it uses type inference to generates subtyping constraints and solve them, akin to unification in HM.

Structures, when combined with loops, enable the construction of nested data (i.e. trees) 
of arbitrary size. To ensure recursive functions on trees are error-free,
systems have used regular tree grammars and recursive types to characterize spaces of trees.
There has been plenty of research on reasoning over regular tree grammars/automata and recursive types \cite{}.
Most relevant to our system is previous work on subtyping of recursive types \cite{}.
